Pre-/Post-Trikafta (Prospective)

### 2023-01-19 Christine Chan/Pre-post Trikafta Prospective/pre_post_trikafta_prospective_analysis.Rmd
Update pre_post_trikafta_prospective_analysis.Rmd

```{r setup, include=FALSE}
library(arsenal)
library(tidyverse)
library(performance)
library(cgmanalysis)
library(AGD)
library(pracma)
library(corrplot)
library(knitr)
knitr::opts_chunk$set(echo = FALSE,warning = FALSE)
knitr::opts_knit$set(root.dir = "/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF")
```

@@

>>>>

```{r setup, include=FALSE}
library(arsenal)
library(tidyverse)
library(performance)
library(cgmanalysis)
library(AGD)
library(pracma)
library(corrplot)
library(DiagrammeR)
library(knitr)
knitr::opts_chunk$set(echo = FALSE,warning = FALSE)
knitr::opts_knit$set(root.dir = "/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF")
```

@@

# Flowchart

```{r}
nums = df %>% group_by(Event.Name) %>% count(Group)
ndf <- create_node_df(n=6,
                        type = paste(nums$Event.Name,nums$Group),
                        label = paste(nums$Event.Name,nums$Group),
                        value=nums$n,
                      shape="rectangle",fixedsize=F)
edges = df %>% group_by(Study.ID) %>% 
  summarise(change = paste("Visit 1",Group[Event.Name=="Visit 1"],"->",
                           "Visit 2",Group[Event.Name=="Visit 2"])) %>%
  count(change)
edges$from = match(sapply(strsplit(edges$change," -> "),"[",1),ndf$type)
edges$to = match(sapply(strsplit(edges$change," -> "),"[",2),ndf$type)
edf <-
  create_edge_df(
    from = edges$from,
    to = edges$to,
    rel = "a",
    label=edges$n)

graph <-
  create_graph(
    nodes_df = ndf,
    edges_df = edf,
    attr_theme = "lr")
render_graph(graph)
```
